\documentclass[a4paper]{memoir}
\usepackage{graphicx}
%% Language and font encodings
\usepackage{microtype}
\usepackage[paperheight=88.9mm,paperwidth=63.5mm,margin=5mm]{geometry}
\usepackage{ragged2e}
\usepackage{adjustbox}
\usepackage{pgffor}
\usepackage{emoji}
\usepackage{tikz}
\newcommand{\cardtext}{0-10}
\newcommand{\grouptext}{2-6}
\newcommand{\agetext}{10+}
\newcommand{\clocktext}{20$''$}
\newcommand{\languagecrop}{english_crop}
\newcommand{\colorcount}{6}
\newcommand{\cardtitle}{TWO TOWERS}
\def\colors{0/myyellow, 1/myorange, 2/myred, 3/mypurple, 4/myblue, 5/mygreen}
\begin{document}
{\footnotesize
\input{../../../rule_lib/rule_lib.tex}
\noindent
\textbf{\emoji{arrows-counterclockwise} Setup.} Create \textbf{6 piles of shuffled cards, face up} in the center of the table, one pile per color.
Each player has two spaces in front of them to build their towers.
\\
\\
\noindent
\textbf{\emoji{dart} Goal of the game.} Score the most points! The score of a tower is (last value placed) $\times$ (number of cards in the tower).
\\
\\
\noindent
\textbf{\emoji{video-game} How it works.} Players take turns. On your turn, you can take \textbf{1 or 2 actions (but not 0!)}. Here are your options:
\begin{itemize}
\item\textbf{Take a card} from one of the 6 piles and place it in your hand. 
\\
\emoji{warning} You cannot have more than 3 cards in your hand!
\item\textbf{Place a card} from your hand onto one of your towers. 
\\
\emoji{warning} The placed card must either be of \textbf{the same value}, or \textbf{the same color but with a higher value} than the last card on the tower (no restriction for the first card of a tower).
\end{itemize}
\noindent
\textbf{\emoji{stop-sign} End of the game.}
If you can no longer play, the game ends for you!
The other players get one last turn each before points are tallied.
\\
\\
\noindent
\emoji{pushpin} Cards in the towers are stacked face up and offset so you can clearly see how many there are.
}
\end{document}